Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
More goodness

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Almost fourty percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations. Future measurements will provide further insight into what clones should be refactored to improve the design of software systems.
\end{abstract}

@@

\section{Clone Detection}\label{chap:clonedetection}
As duplication in source code is a serious problem in many software systems, many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}. However, these tools were not yet assessed in terms of automatically refactoring clones.

In this section, we first assess a set of modern clone detection tools for their applicability to this domain. Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools~\cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. \todo{what is insufficient about these two? what triggered the need to reassess clone detectors? where are the four criteria coming from?}

@@

\subsection{CloneRefactor}
None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}. This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}. In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}.

>>>>

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Almost 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations. Future measurements will provide further insight into what clones should be refactored to improve the design of software systems.
\end{abstract}

@@

\section{Clone Detection}\label{chap:clonedetection}
As duplication in source code is a serious problem in many software systems, many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}. However, these tools were not yet assessed in terms of automatically refactoring clones. In this section, we first assess a set of modern clone detection tools for their applicability to this domain. Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools~\cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. \todo{what is insufficient about these two? what triggered the need to reassess clone detectors? where are the four criteria coming from?}

@@

\subsection{CloneRefactor}
None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}. In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}. %An abstract view of the process flow of CloneRefactor is displayed in figure \ref{fig:clonerefactor}

%\begin{figure}[H]
%  \caption{Abstract representation of CloneRefactor.}
%    \includegraphics[width=1\columnwidth]{img/CloneRefactorOverall}
%  \label{fig:clonerefactor}
%\end{figure}
